
\documentclass[11pt]{article}
\usepackage{UF_FRED_paper_style}
\usepackage{xcolor}  % colored text
\usepackage{lipsum}  %% Package to create dummy text (comment or erase before start)
\usepackage{booktabs}  % professional-quality tables
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{emoji}
\usepackage{float}
\usepackage{geometry}


%% ===============================================
%% Setting the line spacing (3 options: only pick one)
% \doublespacing
% \singlespacing
\onehalfspacing
%% ===============================================

\setlength{\droptitle}{-5em} %% Don't touch

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SET THE TITLE
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% TITLE:
\title{Kevin Willer IM 2022 Proposal: Sentiment Analysis Domain Transfer}

% AUTHORS:
\author{Kevin Willer\\% Name author
    \href{mailto:kwiller@uni-potsdam.de}{\texttt{kwiller@uni-potsdam.de}} %% Email author 1
    }

% DATE:
\date{\today}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\section{General}
{\setstretch{.8}
\maketitle

Goal: SA model with good performance in the domains of Crypto and Climate Tweets, which takes into account stances toward entities.

\begin{enumerate}
        \item Using stance detection (or similar) to be able to look at the Tweets in a more fine-grained way and split them up into several sub-statements if they pertain to different entities.

        \item Using DistilBERT \citet{distilbert} which is pre-trained on Twitter data and fine-tuning it on Crypto and Climate data respectively to increase their performance on the Domain-Tweets.
\end{enumerate}

\section{Stance Detection}

evaluate stance towards given entity. \\
example: https://github.com/ZurichNLP/xstance , though not usable for me, no english \\

\section{Entity Recognition}

uses dictionary for entities and synonyms. bad, but could be scraped from coingecko.
name expansion adds to dictionary automatically (prefixed, suffixed forms etc.) \\

Auto-annotate crypto set with info from coingecko: all \$XXX are entities and everything that is in coingecko token list. Fine-tune NER Bert this way? IOB or BILOU Format (see https://colab.research.google.com/github/NielsRogge/Transformers-Tutorials/blob/master/BERT/Custom_Named_Entity_Recognition_with_BERT_only_first_wordpiece.ipynb) \\

Do I have to do this? Just run the auto-annotation code above as final NER. Otherwise my data is highly biased towards the 4 cashtags I scraped Twitter with. This makes fine-tuning a model with this data a stupid endeavor. \\

Next Problem: How do I split according to entity? Or get the sentence which describes the sentiment towards it? Finding entities is easy, deciding what text describes the sentiment is harder. Ask Prof. Stede?

\section{Relation Extraction}
rule-based natural language parser: understands relations of grammar. \\
machine-learning: higher recall, lower precision than rule-based \\

WordNet to identify if crypto is talked about ? fuzzy matching to Coingecko list? Heuristic with \$tag ? \\

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REFERENCES SECTION
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\medskip

\bibliography{references.bib}
\end{document}
